---
title: "Alcohol vs Seat choice"
author: "Rashonda Weathersby"
date: "February 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??


## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(x=Seat,y=alcohol))
```

## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
According to the graph, it seems like alcohol was consumed the least by people sitting in the front seats. The middle seats had quite a few variants on the outside however, it seems not to reach over 40. The back seats reached over 40. 
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=FALSE,outlier.color = "black") + stat_boxplot(geom ='errorbar') + labs(title="Alcohol vs Seat boxplot \n with 2 lines")
```
According to this box plot the front seat is quite low compared to the middle and the back seat. There are some outside variants. 
## Numerical Summarys


```{r}
favstats(alcohol~Seat,data=davisdata)
```
According to the numerical summary, the back row consumed alcohol at the rate of 9.63, compared to the middle that consumed 3.28, and the first row 1.80. 

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The hypotheses concludes that seating could effect the amount of alcohol a person could consumed. The p-value is 9.656 which is quite high which could rule out a null hypothesis.
  


## Conclusions

In conclusion, the question was asked "Is there a difference between the alcohol consumed between the row you choose to sit in?" According to the graph, number summary,and inferential evidence. It appears that seating choices could play a part in how much alcohol you consume. 

